Validation of Visual Statistical Inference, with Application to Linear Models

### 2012-04-05 paper_jasa.tex
updated t dist figure

\begin{table*}[hbtp]
\caption{Comparison of visual inference with existing inference technique}
\centering 
\begin{tabular}{llll} 
\hline
  & Mathematical Inference &  Visual Inference \\ %[0.5ex] % inserts table %heading 
\hline
  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
 & \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

@@

 & \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

 Null Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.15}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.19}{\includegraphics{test_category.pdf}} \end{center} \end{minipage} \\
 & \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{1.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
 Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
\hline 
\end{tabular}
\label{tbl:compare}
\end{table*}

>>>>

\begin{table*}[hbtp]
\caption{Comparison of visual inference with existing inference technique}
\centering 
\begin{tabular}{llll} 
\hline
  & Mathematical Inference &  Visual Inference \\ %[0.5ex] % inserts table %heading 
\hline
  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

@@

 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

 Null Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.55}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.19}{\includegraphics{test_category.pdf}} \end{center} \end{minipage} \\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
 Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
\hline 
\end{tabular}
\label{tbl:compare}
\end{table*}
